---
title: "ERDC Davis Solute Stats"
subtitle: "Linear models for flow, ppt, tsm and solute concentrations" 
author: "Kelly Loria"
date: "`r Sys.Date()`"
output:
  github_document:
    toc: true
  pdf_document: 
    toc: true
  html_document:
    theme: united
    highlight: tango
    toc: true
    toc_float: true
    code_folding: hide
    self_contained: true
editor_options:
  markdown:
    wrap: 72
---

```{=html}
<style type="text/css">
body, td {font-size: 12px;}
code.r{font-size: 8px;}
pre {font-size: 10px}
</style>
```

```{r setup, include=FALSE}
# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,           # Hide code by default
  warning = FALSE,
  message = FALSE,
  cache = TRUE,           # Enable caching for all chunks
  cache.path = "_cache/", # Organized cache directory
  fig.path = "figures/",  # Save figures to dedicated folder
  fig.width = 7,
  fig.height = 3,
  fig.retina = 2,
  out.width = "80%"
)

# Font size hook (kept from original)
def.chunk.hook <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", 
         paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})

# Set parallel processing options for brms
options(mc.cores = parallel::detectCores() - 1)  # Leave one core free
```

```{r packages, include=FALSE}
# Load all required packages once
# Core data manipulation
library(tidyverse)
library(lubridate)
library(here)  # For portable file paths

# Statistical modeling
library(lme4)
library(lmerTest)
library(brms)
library(MuMIn)
library(PerformanceAnalytics)
library(loo)

# Data import
library(readxl)
library(dataRetrieval)

# Visualization
library(viridis)
library(cowplot)
library(ggpubr)
library(ggpmisc)

# Tables
library(knitr)
library(kableExtra)

# Utilities
library(zoo)
library(slider)
library(broom)
```

```{r site_colors, include=FALSE}
# Define color schemes
site_colors <- c(
  "ophir" = "#7d5ba6",
  "winters_usgs" = "#4287f5",
  "winters_up" = "#7fc5f0",
  "davis" = "#d9cb7c",
  "browns" = "#c94d00", 
  "browns_sub" = "#bd772d"
)

site_colors_OL <- c(
  "A_ophir" = "#7d5ba6",
  "F_winters_usgs" = "#4287f5",
  "E_winters_up" = "#7fc5f0",
  "B_davis" = "#d9cb7c",
  "D_browns" = "#c94d00",
  "C_browns_sub" = "#bd772d"
)

ref_date <- as.Date("2024-09-25")
```

```{r functions, include=FALSE}
# Water year function
water_year <- function(data) {
  data %>%
    mutate(date = ymd(date)) %>%
    mutate(WaterYear = if_else(month(date) >= 10, year(date) + 1, year(date)))
}

# Function to fit or load Bayesian models
fit_brm <- function(model_name, formula, data, family, prior, 
                            chains = 3, cores = 3, iter = 3000,
                            warmup = 1500, refit = FALSE) {
  
  # Create models directory if it doesn't exist
  model_dir <- here("models")
  if (!dir.exists(model_dir)) {
    dir.create(model_dir, recursive = TRUE)
  }
  
  model_file <- here("models", paste0(model_name, ".rds"))
  
  if (file.exists(model_file) && !refit) {
    message("Loading cached model: ", model_name)
    return(readRDS(model_file))
  }
  
  message("Fitting model: ", model_name, " (this may take 10-20 minutes)")
  
  m <- brm(
    formula, 
    data = data, 
    family = family, 
    prior = prior,
    chains = chains, 
    cores = cores, 
    iter = iter, 
    warmup = warmup,
    thin = 1,
    seed = 122  # For reproducibility
  )
  
  saveRDS(m, model_file)
  message("Model saved to: ", model_file)
  
  return(m)
}
```

```{r data_paths, include=FALSE}
# Option 1: Use here() for project-relative paths (recommended)
# data_dir <- here()

# Option 2: Set absolute path (less portable)
data_dir <- "/Users/kellyloria/Documents/DRI/ERDC_Davis_Fire"

# Define subdirectories
proc_data_dir <- file.path(data_dir, "Processes_data")
raw_data_dir <- file.path(data_dir, "Raw_data")
fig_dir <- file.path(data_dir, "Figures")
```

```{r load_chem_data, cache=TRUE, include=FALSE}
# Load chemistry data
test_dat <- read.csv(file.path(proc_data_dir, "ERDC_water_only_chem_dat_processed.csv")) %>%
  select(-site) %>%   
  rename(site = site_lab) %>%  
  filter(site != "davis") %>%
  mutate(
    date = as.Date(date),
    datetime = as.POSIXct(datetime),
    burn_area = case_when(
      site == "ophir" ~ 0,
      site == "winters_usgs" ~ 65,
      site == "winters_up" ~ 62,
      site == "browns" ~ 42, 
      site == "browns_sub" ~ 41
    )
  ) %>%
  mutate(Sr_B_QC = Sr_QC / B_QC)
```

```{r load_tss_data, cache=TRUE, dependson="load_chem_data", include=FALSE}
# Load and process TSS data
tss_dat2 <- read_csv(file.path(raw_data_dir, "TSS_data.csv")) %>%
  filter(site != "davis" | site != "ophir") %>%
  mutate(
    date = as.Date(Collection_date, format = "%m/%d/%y"),
    TSS_mgL = parse_number(as.character(TSS_mgL))
  ) %>%
  select(site, date, TSS_mgL)

# Average TSS_mgL for each site-date
tss_mean <- tss_dat2 %>%
  group_by(site, date) %>%
  summarise(TSS_mgL = mean(TSS_mgL, na.rm = TRUE), .groups = "drop") %>%
  mutate(TSS_mgL = ifelse(is.nan(TSS_mgL), NA_real_, TSS_mgL))

# Merge chemistry and TSS data
merged_df <- test_dat %>%
  left_join(tss_mean, by = c("site", "date")) %>%
  mutate(
    TSS = as.numeric(TSS),
    TSS = coalesce(TSS, TSS_mgL)
  ) %>%
  select(-TSS_mgL)
```


```{r load_hydro_data, cache=TRUE, dependson="load_hydro_data", include=FALSE}
# hydro data

flow_dat <-  read_csv(file.path(proc_data_dir, "ERDC_water_hourlyflow.csv")) %>%
  mutate(date=as.Date(date)) %>%  filter((site!="davis" | site!="ophir")) %>%
    mutate(Name = case_when(
    site == "winters_usgs" ~ "winters",
    site == "winters_up" ~ "winters",
    site == "browns" ~ "browns", 
    site == "browns_sub" ~ "browns"))

str(flow_dat)

# Load precipitation data
ppt_dat <- read_csv(file.path(raw_data_dir, "prism_cat_new.csv")) %>%
  filter((Name!="davis" | Name!="ophir")) %>%
  mutate(
    date = as.Date(Date, format = "%Y-%m-%d"),
    lagPPT = lag(ppt..mm.),
    lag_C_PPT = ppt..mm. + lagPPT) %>%
  dplyr::select(Name, date, ppt..mm., lag_C_PPT)

hydro_combined <-flow_dat %>%
  left_join(ppt_dat, by=c("date", "Name")) 

glimpse(hydro_combined)


new_df_hydro <- hydro_combined %>%
  arrange(site, date) %>%
  group_by(site) %>%
  mutate(flow_filled = zoo::na.approx(flow, x = date, na.rm = FALSE)) %>%
  ungroup()

```


```{r data_prep, cache=TRUE, dependson="load_tss_data", include=FALSE}
# Prepare data for plotting and modeling
df_WQ_plot <- merged_df %>%
  mutate(
    burn_area = case_when(
      site == "ophir" ~ 0,
      site == "winters_usgs" ~ 65,
      site == "winters_up" ~ 62,
      site == "browns" ~ 42, 
      site == "browns_sub" ~ 41
    ),
    site_lab = fct_reorder(site, burn_area, .fun = min, .desc = FALSE),
    tsf = as.integer(difftime(datetime, ref_date, units = "days")) 
  ) 
```

## Data Summary

For all burned locations.

```{r data_summary, echo=FALSE, include=TRUE}
# Basic summary of loaded data
summary_stats <- df_WQ_plot %>%
  group_by(site) %>%
  summarise(
    n_samples = n(),
    date_range = paste(min(date, na.rm = TRUE), "to", max(date, na.rm = TRUE)),
    burn_area_pct = first(burn_area)
  )

kable(summary_stats, 
      caption = "Summary of water quality sampling by site",
      col.names = c("Site", "N Samples", "Date Range", "Burn Area (%)"))
```

## Exploratory Analysis

### Covariate Relationships

```{r covar_prep, cache=TRUE, dependson="data_prep", include=FALSE}


vars <- c("TSS", "lag_C_PPT", "tsf", "flow_filled", "temp", "DO", "EC", "pH", "site")

df_model <- df_WQ_plot %>%
  left_join(new_df_hydro, by = c("site", "date")) %>%
  filter(site != "ophir") %>%
  select(all_of(vars)) %>%
  drop_na() %>%
  mutate(
    catchment = case_when(
      site == "winters_usgs" ~ "winters",
      site == "winters_up" ~ "winters",
      site == "browns" ~ "browns",
      site == "browns_sub" ~ "browns"
    )
  )
```

```{r correlation_plot,echo=FALSE, include=TRUE, fig.width=10, fig.height=10}
# Correlation matrix (only runs if df_model exists)
covar_check <- df_model[, c(1:8)]
chart.Correlation(covar_check, histogram = TRUE, pch = 19)
```

## Statistical Models

### Frequentist Mixed Models (Precipitation)

```{r ppt_models, cache=TRUE, dependson="covar_prep", include=FALSE}
# Fit multiple precipitation models for comparison
ppt_mod <- lmer(TSS ~ scale(lag_C_PPT) + scale(tsf) + 
                scale(lag_C_PPT*tsf) + (1 | catchment/site), data = df_model)

ppt_mod.1 <- lmer(TSS ~ scale(lag_C_PPT) + scale(tsf) + 
                  (1 | catchment/site), data = df_model)

ppt_mod.2 <- lmer(TSS ~ scale(lag_C_PPT) + scale(tsf) + scale(flow_filled) + 
                  (1 | catchment/site), data = df_model)

ppt_mod.3 <- lmer(TSS ~ scale(lag_C_PPT) + scale(tsf) + 
                  scale(flow_filled*tsf) + (1 | catchment/site), data = df_model)

ppt_mod.4 <- lmer(TSS ~ scale(lag_C_PPT) + (1 | catchment/site), data = df_model)

ppt_mod.5 <- lmer(TSS ~ scale(lag_C_PPT) + scale(flow_filled) + 
                  (1 | catchment/site), data = df_model)
```

```{r ppt_model_selection, echo=FALSE, include=TRUE}
# Model comparison
aic_table <- AIC(ppt_mod, ppt_mod.1, ppt_mod.2, ppt_mod.3, ppt_mod.4, ppt_mod.5)
kable(aic_table, caption = "AIC comparison of precipitation models", digits = 2)

# Model selection table
sel_table <- model.sel(ppt_mod, ppt_mod.1, ppt_mod.2, ppt_mod.3, 
                       ppt_mod.4, ppt_mod.5, rank = "AICc")
kable(sel_table, caption = "Model selection based on AICc", digits = 2)
```

**Best model: ppt_mod.2** (TSS ~ PPT + TSF + Flow)

Rationale:

- ΔAICc difference trivial from ppt_mod.2 to the interaction models (ppt_mod and ppt_mod.3)

- Interaction unsupported and more complex in ppt_mod

- Strong collinearity (r = −0.871) in ppt_mod

### Bayesian Models

#### Model Setup

```{r bayes_priors_TSS, cache=TRUE, dependson="covar_prep",  include=FALSE}
# Define priors for TSS lognormal model
mu0_TSS <- round(log(mean(df_model$TSS, na.rm = TRUE)), 2)

priors_logn_TSS <- c(
  set_prior(sprintf("normal(%f, 2)", mu0_TSS), class = "Intercept"),
  set_prior("normal(0, 1)", class = "b"),
  set_prior("exponential(1)", class = "sd"),
  set_prior("exponential(1)", class = "sigma")
)
```

#### TSS Model

```{r TSS_bayes_fit, cache=TRUE, dependson="bayes_priors_TSS", include=FALSE}
# Fit or load TSS Bayesian model
TSS_m_logn <- fit_brm(
  model_name = "TSS_lognormal",
  formula = TSS ~ scale(lag_C_PPT) + scale(tsf) + scale(flow_filled) +
                  catchment + (1 | catchment:site),
  data = df_model,
  family = lognormal(),
  prior = priors_logn_TSS)

# 
# TSS_m_logn_AR2 <- fit_brm(
#   model_name = "TSS_lognormal_ar2",
#   formula = bf(
#     TSS ~ scale(lag_C_PPT) + scale(tsf) +
#       scale(lag_C_PPT) * scale(tsf) +
#       scale(flow_filled) * scale(tsf) + 
#       catchment + (1 | catchment:site)),
#   data = df_model,
#   family = lognormal(),
#   prior = priors_logn_TSS,
#   chains = 3,
#   cores = 3,
#   iter = 4000,
#   warmup = 2000
# )

```

```{r TSS_diagnostics, include=TRUE, echo=FALSE, fig.width=10, fig.height=6}
# Trace plots
plot(TSS_m_logn)
```

```{r TSS_pp_checks,include=TRUE, echo=FALSE, fig.width=10, fig.height=4}

# Posterior predictive checks
pp_check(TSS_m_logn, ndraws = 100)
# pp_check(TSS_m_logn, type = "hist", ndraws = 5)
```

```{r TSS_results,include=TRUE, echo=FALSE}
library(loo)
# Model summary
summary(TSS_m_logn)

# LOO cross-validation
loo_TSS <- brms::loo(TSS_m_logn)
print(loo_TSS)


#loo_TSS_AR2 <- brms::loo(TSS_m_logn_AR2)

# Bayesian R²
r2_TSS <- bayes_R2(TSS_m_logn)
#kable(r2_TSS, caption = "Bayesian R² for TSS Model", digits = 3)


#loo_compare(loo_TSS, loo_TSS_AR2)
```

```{r TSS_effects_extract, cache=TRUE, dependson="TSS_bayes_fit",  include=FALSE}
# Extract effects and confidence intervals
post_TSS <- posterior_summary(TSS_m_logn, pars = "^b_",  probs = c(0.05, 0.95))

effects_df_TSS <- data.frame(
  term = gsub("^b_", "", rownames(post_TSS)),
  estimate = post_TSS[, "Estimate"],
  l90 = post_TSS[, "Q5"],
  u90 = post_TSS[, "Q95"]
) %>%
  mutate(
    estimate_exp = exp(estimate),
    l90_exp = exp(l90),
    u90_exp = exp(u90),
    analyte = "TSS",
    bayes_R2 = mean(bayes_R2(TSS_m_logn)[, "Estimate"])
  )
```

```{r TSS_effects_table,  echo=FALSE}
# Display effects table
kable(effects_df_TSS %>% select(-analyte), 
      caption = "TSS Model Effects (Log and Exponentiated Scale)",
      digits = 2)
```

```{r TSS_effects_plot, include=FALSE, echo=FALSE, fig.width=8, fig.height=4}
# Plot effects
effects_df_TSS %>%
  filter(term != "Intercept") %>%
  ggplot(aes(x = estimate_exp, y = term)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = l90_exp, xmax = u90_exp), width = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Multiplicative effect (exp(β))",
    y = NULL,
    title = "TSS Model: Effect Sizes",
    subtitle = sprintf("Bayesian R² = %.2f", unique(effects_df_TSS$bayes_R2))
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )
```

Look at solute with TSS, PPT, and flow 

```{r TSS_plot, include=T, echo=FALSE, fig.width=10, fig.height=3}
# Plot effects
tsf_plot <- df_model %>%
  ggplot(aes(y = TSS, x = tsf)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "Days since fire",
    y = "TSS") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

PPT_plot <- df_model %>%
  ggplot(aes(y = TSS, x = lag_C_PPT)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "PPT",
    y = "TSS") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

fow_plot <- df_model %>%
  ggplot(aes(y = TSS, x = flow_filled)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "flow",
    y = "TSS") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

covar_grid <- ggarrange( 
  tsf_plot,
  PPT_plot,
  fow_plot,
  common.legend = T,
  ncol=3,
  nrow=1)

covar_grid

```



#### DOC Model

```{r covar_prep_DOC, cache=TRUE, dependson="data_prep", include=FALSE}


vars <- c("DOC_QC", "lag_C_PPT", "tsf", "flow_filled", "temp", "DO", "EC", "pH", "site")

df_model <- df_WQ_plot %>%
  left_join(new_df_hydro, by = c("site", "date")) %>%
  filter(site != "ophir") %>%
  select(all_of(vars)) %>%
  drop_na() %>%
  mutate(
    catchment = case_when(
      site == "winters_usgs" ~ "winters",
      site == "winters_up" ~ "winters",
      site == "browns" ~ "browns",
      site == "browns_sub" ~ "browns"
    )
  )
```




```{r bayes_priors_DOC, cache=TRUE, dependson="covar_prep", include=FALSE}

mu0_DOC <- round(log(mean(df_model$DOC_QC, na.rm = TRUE)), 2)

priors_logn_DOC <- c(
  set_prior(sprintf("normal(%f, 2)", mu0_DOC), class = "Intercept"),
  set_prior("normal(0, 1)", class = "b"),
  set_prior("exponential(1)", class = "sd"),
  set_prior("exponential(1)", class = "sigma")
)
```


```{r DOC_bayes_fit, cache=TRUE, dependson="bayes_priors_DOC", include=FALSE}
# Fit or load DOC Bayesian model
DOC_m_logn <- fit_brm(
  model_name = "DOC_lognormal",
  formula = DOC_QC ~ scale(lag_C_PPT) + scale(tsf) + scale(flow_filled) +
                  catchment + (1 | catchment:site),
  data = df_model,
  family = lognormal(),
  prior = priors_logn_DOC
)
```

```{r DOC_diagnostics, include=TRUE, echo=FALSE, fig.width=10, fig.height=6}
# Trace plots
plot(DOC_m_logn)
```

```{r DOC_pp_checks,include=TRUE, echo=FALSE, fig.width=10, fig.height=4}
# Posterior predictive checks
pp_check(DOC_m_logn, ndraws = 100)
# pp_check(DOC_m_logn, type = "hist", ndraws = 5)
```

```{r DOC_results,include=TRUE, echo=FALSE}
library(loo)
# Model summary
summary(DOC_m_logn)

# LOO cross-validation
loo_DOC <- brms::loo(DOC_m_logn)
print(loo_DOC)

# Bayesian R²
r2_DOC <- bayes_R2(DOC_m_logn)
#kable(r2_DOC, caption = "Bayesian R² for DOC Model", digits = 2)
```

```{r DOC_effects_extract, cache=TRUE, dependson="DOC_bayes_fit",  include=FALSE}
# Extract effects and confidence intervals
post_DOC <- posterior_summary(DOC_m_logn, pars = "^b_", probs = c(0.05, 0.95))

effects_df_DOC <- data.frame(
  term = gsub("^b_", "", rownames(post_DOC)),
  estimate = post_DOC[, "Estimate"],
  l90 = post_DOC[, "Q5"],
  u90 = post_DOC[, "Q95"]
) %>%
  mutate(
    estimate_exp = exp(estimate),
    l90_exp = exp(l90),
    u90_exp = exp(u90),
    analyte = "DOC",
    bayes_R2 = mean(bayes_R2(DOC_m_logn)[, "Estimate"])
  )
```

```{r DOC_effects_table,  echo=FALSE}
# Display effects table
kable(effects_df_DOC %>% select(-analyte), 
      caption = "DOC Model Effects (Log and Exponentiated Scale)",
      digits = 2)
```

```{r DOC_effects_plot_DOC, include=FALSE, echo=FALSE, fig.width=8, fig.height=4}
# Plot effects
effects_df_DOC %>%
  filter(term != "Intercept") %>%
  ggplot(aes(x = estimate_exp, y = term)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = l90_exp, xmax = u90_exp), width = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Multiplicative effect (exp(β))",
    y = NULL,
    title = "DOC Model: Effect Sizes",
    subtitle = sprintf("Bayesian R² = %.2f", unique(effects_df_DOC$bayes_R2))
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )
```




Look at solute with TSF, PPT, and flow 

```{r DOC_effects_plot, include=T, echo=FALSE, fig.width=10, fig.height=3}
# Plot effects
tsf_plot <- df_model %>%
  ggplot(aes(y = DOC_QC, x = tsf)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "Days since fire",
    y = "DOC") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

PPT_plot <- df_model %>%
  ggplot(aes(y = DOC_QC, x = lag_C_PPT)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "PPT",
    y = "DOC") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

fow_plot <- df_model %>%
  ggplot(aes(y = DOC_QC, x = flow_filled)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "flow",
    y = "DOC") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

covar_grid <- ggarrange( 
  tsf_plot,
  PPT_plot,
  fow_plot,
  common.legend = T,
  ncol=3,
  nrow=1)

covar_grid

```

#### TDN Model

```{r covar_prep_TDN, cache=TRUE, dependson="data_prep", include=FALSE}

vars <- c("TDN_QC", "lag_C_PPT", "tsf", "flow_filled", "temp", "DO", "EC", "pH", "site")

df_model <- df_WQ_plot %>%
  left_join(new_df_hydro, by = c("site", "date")) %>%
  filter(site != "ophir") %>%
  select(all_of(vars)) %>%
  drop_na() %>%
  mutate(
    catchment = case_when(
      site == "winters_usgs" ~ "winters",
      site == "winters_up" ~ "winters",
      site == "browns" ~ "browns",
      site == "browns_sub" ~ "browns"
    )
  )
```


```{r bayes_priors_TDN, cache=TRUE, dependson="covar_prep",  include=FALSE}

mu0_TDN <- round(log(mean(df_model$TDN_QC, na.rm = TRUE)), 2)

priors_logn_TDN <- c(
  set_prior(sprintf("normal(%f, 2)", mu0_TDN), class = "Intercept"),
  set_prior("normal(0, 1)", class = "b"),
  set_prior("exponential(1)", class = "sd"),
  set_prior("exponential(1)", class = "sigma")
)
```


```{r TDN_bayes_fit, cache=TRUE, dependson="bayes_priors_TDN", include=FALSE}
# Fit or load TDN Bayesian model
TDN_m_logn <- fit_brm(
  model_name = "TDN_lognormal",
  formula = TDN_QC ~ scale(lag_C_PPT) + scale(tsf) + scale(flow_filled) +
                  catchment + (1 | catchment:site),
  data = df_model,
  family = lognormal(),
  prior = priors_logn_TDN
)
```

```{r TDN_diagnostics, include=TRUE, echo=FALSE, fig.width=10, fig.height=6}
# Trace plots
plot(TDN_m_logn)
```

```{r TDN_pp_checks,include=TRUE, echo=FALSE, fig.width=10, fig.height=4}
# Posterior predictive checks
pp_check(TDN_m_logn, ndraws = 100)
# pp_check(TDN_m_logn, type = "hist", ndraws = 5)
```

```{r TDN_results,include=TRUE, echo=FALSE}
library(loo)
# Model summary
summary(TDN_m_logn)

# LOO cross-validation
loo_TDN <- brms::loo(TDN_m_logn)
print(loo_TDN)

# Bayesian R²
r2_TDN <- bayes_R2(TDN_m_logn)
#kable(r2_TDN, caption = "Bayesian R² for TDN Model", digits = 3)
```

```{r TDN_effects_extract, cache=TRUE, dependson="TDN_bayes_fit",  include=FALSE}
# Extract effects and confidence intervals
post_TDN <- posterior_summary(TDN_m_logn, pars = "^b_", probs = c(0.05, 0.95))

effects_df_TDN <- data.frame(
  term = gsub("^b_", "", rownames(post_TDN)),
  estimate = post_TDN[, "Estimate"],
  l90 = post_TDN[, "Q5"],
  u90 = post_TDN[, "Q95"]
) %>%
  mutate(
    estimate_exp = exp(estimate),
    l90_exp = exp(l90),
    u90_exp = exp(u90),
    analyte = "TDN",
    bayes_R2 = mean(bayes_R2(TDN_m_logn)[, "Estimate"])
  )
```

```{r TDN_effects_table,  echo=FALSE}
# Display effects table
kable(effects_df_TDN %>% select(-analyte), 
      caption = "TDN Model Effects (Log and Exponentiated Scale)",
      digits = 2)
```

```{r TDN_effects_plot, include=FALSE, echo=FALSE, fig.width=8, fig.height=4}
# Plot effects
effects_df_TDN %>%
  filter(term != "Intercept") %>%
  ggplot(aes(x = estimate_exp, y = term)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = l90_exp, xmax = u90_exp), width = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Multiplicative effect (exp(β))",
    y = NULL,
    title = "TDN Model: Effect Sizes",
    subtitle = sprintf("Bayesian R² = %.2f", unique(effects_df_TDN$bayes_R2))
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )
```


Look at solute with TSF, PPT, and flow 

```{r TDN_plot, include=T, echo=FALSE, fig.width=10, fig.height=3}
# Plot effects
tsf_plot <- df_model %>%
  ggplot(aes(y = TDN_QC, x = tsf)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "Days since fire",
    y = "TDN") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

PPT_plot <- df_model %>%
  ggplot(aes(y = TDN_QC, x = lag_C_PPT)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "PPT",
    y = "TDN") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

fow_plot <- df_model %>%
  ggplot(aes(y = TDN_QC, x = flow_filled)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "flow",
    y = "TDN") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

covar_grid <- ggarrange( 
  tsf_plot,
  PPT_plot,
  fow_plot,
  common.legend = T,
  ncol=3,
  nrow=1)

covar_grid

```



#### PO4.P Model

```{r covar_prep_PO4.P, cache=TRUE, dependson="data_prep", include=FALSE}

vars <- c("PO4.P_QC", "lag_C_PPT", "tsf", "flow_filled", "temp", "DO", "EC", "pH", "site")

df_model <- df_WQ_plot %>%
  left_join(new_df_hydro, by = c("site", "date")) %>%
  filter(site != "ophir") %>%
  select(all_of(vars)) %>%
  drop_na() %>%
  mutate(
    catchment = case_when(
      site == "winters_usgs" ~ "winters",
      site == "winters_up" ~ "winters",
      site == "browns" ~ "browns",
      site == "browns_sub" ~ "browns"
    )
  )
```


```{r bayes_priors_PO4.P, cache=TRUE, dependson="covar_prep",  include=FALSE}

mu0_PO4.P <- round(log(mean(df_model$PO4.P_QC, na.rm = TRUE)), 2)

priors_logn_PO4.P <- c(
  set_prior(sprintf("normal(%f, 2)", mu0_PO4.P), class = "Intercept"),
  set_prior("normal(0, 1)", class = "b"),
  set_prior("exponential(1)", class = "sd"),
  set_prior("exponential(1)", class = "sigma")
)
```


```{r PO4.P_bayes_fit, cache=TRUE, dependson="bayes_priors_PO4.P", include=FALSE}
# Fit or load PO4.P Bayesian model
PO4.P_m_logn <- fit_brm(
  model_name = "PO4.P_lognormal",
  formula = PO4.P_QC ~ scale(lag_C_PPT) + scale(tsf) + scale(flow_filled) +
                  catchment + (1 | catchment:site),
  data = df_model,
  family = lognormal(),
  prior = priors_logn_PO4.P
)
```

```{r PO4.P_diagnostics, include=TRUE, echo=FALSE, fig.width=10, fig.height=6}
# Trace plots
plot(PO4.P_m_logn)
```

```{r PO4.P_pp_checks,include=TRUE, echo=FALSE, fig.width=10, fig.height=4}
# Posterior predictive checks
pp_check(PO4.P_m_logn, ndraws = 100)
# pp_check(PO4.P_m_logn, type = "hist", ndraws = 5)
```

```{r PO4.P_results,include=TRUE, echo=FALSE}
library(loo)
# Model summary
summary(PO4.P_m_logn)

# LOO cross-validation
loo_PO4.P <- brms::loo(PO4.P_m_logn)
print(loo_PO4.P)

# Bayesian R²
r2_PO4.P <- bayes_R2(PO4.P_m_logn)
##kable(r2_PO4.P, caption = "Bayesian R² for PO4.P Model", digits = 3)
```

```{r PO4.P_effects_extract, cache=TRUE, dependson="PO4.P_bayes_fit",  include=FALSE}
# Extract effects and confidence intervals
post_PO4.P <- posterior_summary(PO4.P_m_logn, pars = "^b_", probs = c(0.05, 0.95))

effects_df_PO4.P <- data.frame(
  term = gsub("^b_", "", rownames(post_PO4.P)),
  estimate = post_PO4.P[, "Estimate"],
  l90 = post_PO4.P[, "Q5"],
  u90 = post_PO4.P[, "Q95"]
) %>%
  mutate(
    estimate_exp = exp(estimate),
    l90_exp = exp(l90),
    u90_exp = exp(u90),
    analyte = "PO4.P",
    bayes_R2 = mean(bayes_R2(PO4.P_m_logn)[, "Estimate"])
  )
```

```{r PO4.P_effects_table,  echo=FALSE}
# Display effects table
kable(effects_df_PO4.P %>% select(-analyte), 
      caption = "PO4.P Model Effects (Log and Exponentiated Scale)",
      digits = 2)
```

```{r PO4.P_effects_plot, include=FALSE, echo=FALSE, fig.width=8, fig.height=4}
# Plot effects
effects_df_PO4.P %>%
  filter(term != "Intercept") %>%
  ggplot(aes(x = estimate_exp, y = term)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = l90_exp, xmax = u90_exp), width = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Multiplicative effect (exp(β))",
    y = NULL,
    title = "PO4.P Model: Effect Sizes",
    subtitle = sprintf("Bayesian R² = %.2f", unique(effects_df_PO4.P$bayes_R2))
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )
```


Look at solute with TSF, PPT, and flow 

```{r PO4_plot, include=T, echo=FALSE, fig.width=10, fig.height=3}
# Plot effects
tsf_plot <- df_model %>%
  ggplot(aes(y = PO4.P_QC, x = tsf)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "Days since fire",
    y = "PO4.P") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

PPT_plot <- df_model %>%
  ggplot(aes(y = PO4.P_QC, x = lag_C_PPT)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "PPT",
    y = "PO4.P") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

fow_plot <- df_model %>%
  ggplot(aes(y = PO4.P_QC, x = flow_filled)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "flow",
    y = "PO4.P") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

covar_grid <- ggarrange( 
  tsf_plot,
  PPT_plot,
  fow_plot,
  common.legend = T,
  ncol=3,
  nrow=1)

covar_grid

```



#### Sr Model

```{r covar_prep_Sr, cache=TRUE, dependson="data_prep", include=FALSE}

vars <- c("Sr_QC", "lag_C_PPT", "tsf", "flow_filled", "temp", "DO", "EC", "pH", "site")

df_model <- df_WQ_plot %>%
  left_join(new_df_hydro, by = c("site", "date")) %>%
  filter(site != "ophir") %>%
  select(all_of(vars)) %>%
  drop_na() %>%
  mutate(
    catchment = case_when(
      site == "winters_usgs" ~ "winters",
      site == "winters_up" ~ "winters",
      site == "browns" ~ "browns",
      site == "browns_sub" ~ "browns"
    )
  )
```


```{r bayes_priors_Sr, cache=TRUE, dependson="covar_prep",  include=FALSE}

mu0_Sr <- round(log(mean(df_model$Sr_QC, na.rm = TRUE)), 2)

priors_logn_Sr <- c(
  set_prior(sprintf("normal(%f, 2)", mu0_Sr), class = "Intercept"),
  set_prior("normal(0, 1)", class = "b"),
  set_prior("exponential(1)", class = "sd"),
  set_prior("exponential(1)", class = "sigma")
)
```


```{r Sr_bayes_fit, cache=TRUE, dependson="bayes_priors_Sr", include=FALSE}
# Fit or load Sr Bayesian model
Sr_m_logn <- fit_brm(
  model_name = "Sr_lognormal",
  formula = Sr_QC ~ scale(lag_C_PPT) + scale(tsf) + scale(flow_filled) +
                  catchment + (1 | catchment:site),
  data = df_model,
  family = lognormal(),
  prior = priors_logn_Sr
)
```

```{r Sr_diagnostics, include=TRUE, echo=FALSE, fig.width=10, fig.height=6}
# Trace plots
plot(Sr_m_logn)
```

```{r Sr_pp_checks,include=TRUE, echo=FALSE, fig.width=10, fig.height=4}
# Posterior predictive checks
pp_check(Sr_m_logn, ndraws = 100)
# pp_check(Sr_m_logn, type = "hist", ndraws = 5)
```

```{r Sr_results,include=TRUE, echo=FALSE}
library(loo)
# Model summary
summary(Sr_m_logn)

# LOO cross-validation
loo_Sr <- brms::loo(Sr_m_logn)
print(loo_Sr)

# Bayesian R²
r2_Sr <- bayes_R2(Sr_m_logn)
#kable(r2_Sr, caption = "Bayesian R² for Sr Model", digits = 3)
```

```{r Sr_effects_extract, cache=TRUE, dependson="Sr_bayes_fit",  include=FALSE}
# Extract effects and confidence intervals
post_Sr <- posterior_summary(Sr_m_logn, pars = "^b_", probs = c(0.05, 0.95))

effects_df_Sr <- data.frame(
  term = gsub("^b_", "", rownames(post_Sr)),
  estimate = post_Sr[, "Estimate"],
  l90 = post_Sr[, "Q5"],
  u90 = post_Sr[, "Q95"]
) %>%
  mutate(
    estimate_exp = exp(estimate),
    l90_exp = exp(l90),
    u90_exp = exp(u90),
    analyte = "Sr",
    bayes_R2 = mean(bayes_R2(Sr_m_logn)[, "Estimate"])
  )
```

```{r Sr_effects_table,  echo=FALSE}
# Display effects table
kable(effects_df_Sr %>% select(-analyte), 
      caption = "Sr Model Effects (Log and Exponentiated Scale)",
      digits = 2)
```

```{r Sr_effects_plot, include=FALSE, echo=FALSE, fig.width=8, fig.height=4}
# Plot effects
effects_df_Sr %>%
  filter(term != "Intercept") %>%
  ggplot(aes(x = estimate_exp, y = term)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = l90_exp, xmax = u90_exp), width = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Multiplicative effect (exp(β))",
    y = NULL,
    title = "Sr Model: Effect Sizes",
    subtitle = sprintf("Bayesian R² = %.2f", unique(effects_df_Sr$bayes_R2))
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )
```


Look at solute with TSF, PPT, and flow 

```{r Sr_plot, include=T, echo=FALSE, fig.width=10, fig.height=3}
# Plot effects
tsf_plot <- df_model %>%
  ggplot(aes(y = Sr_QC, x = tsf)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "Days since fire",
    y = "Sr") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

PPT_plot <- df_model %>%
  ggplot(aes(y = Sr_QC, x = lag_C_PPT)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "PPT",
    y = "Sr") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

fow_plot <- df_model %>%
  ggplot(aes(y = Sr_QC, x = flow_filled)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "flow",
    y = "Sr") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

covar_grid <- ggarrange( 
  tsf_plot,
  PPT_plot,
  fow_plot,
  common.legend = T,
  ncol=3,
  nrow=1)

covar_grid

```



#### Fe Model

```{r covar_prep_Fe, cache=TRUE, dependson="data_prep", include=FALSE}

vars <- c("Fe_QC", "lag_C_PPT", "tsf", "flow_filled", "temp", "DO", "EC", "pH", "site")

df_model <- df_WQ_plot %>%
  left_join(new_df_hydro, by = c("site", "date")) %>%
  filter(site != "ophir") %>%
  select(all_of(vars)) %>%
  drop_na() %>%
  mutate(
    catchment = case_when(
      site == "winters_usgs" ~ "winters",
      site == "winters_up" ~ "winters",
      site == "browns" ~ "browns",
      site == "browns_sub" ~ "browns"
    )
  )
```


```{r bayes_priors_Fe, cache=TRUE, dependson="covar_prep",  include=FALSE}

mu0_Fe <- round(log(mean(df_model$Fe_QC, na.rm = TRUE)), 2)

priors_logn_Fe <- c(
  set_prior(sprintf("normal(%f, 2)", mu0_Fe), class = "Intercept"),
  set_prior("normal(0, 1)", class = "b"),
  set_prior("exponential(1)", class = "sd"),
  set_prior("exponential(1)", class = "sigma")
)
```


```{r Fe_bayes_fit, cache=TRUE, dependson="bayes_priors_Fe", include=FALSE}
# Fit or load Fe Bayesian model
Fe_m_logn <- fit_brm(
  model_name = "Fe_lognormal",
  formula = Fe_QC ~ scale(lag_C_PPT) + scale(tsf) + scale(flow_filled) +
                  catchment + (1 | catchment:site),
  data = df_model,
  family = lognormal(),
  prior = priors_logn_Fe
)
```

```{r Fe_diagnostics, include=TRUE, echo=FALSE, fig.width=10, fig.height=6}
# Trace plots
plot(Fe_m_logn)
```

```{r Fe_pp_checks,include=TRUE, echo=FALSE, fig.width=10, fig.height=4}
# Posterior predictive checks
pp_check(Fe_m_logn, ndraws = 100)
# pp_check(Fe_m_logn, type = "hist", ndraws = 5)
```

```{r Fe_results,include=TRUE, echo=FALSE}
library(loo)
# Model summary
summary(Fe_m_logn)

# LOO cross-validation
loo_Fe <- brms::loo(Fe_m_logn)
print(loo_Fe)

# Bayesian R²
r2_Fe <- bayes_R2(Fe_m_logn)
#kable(r2_Fe, caption = "Bayesian R² for Fe Model", digits = 3)
```

```{r Fe_effects_extract, cache=TRUE, dependson="Fe_bayes_fit",  include=FALSE}
# Extract effects and confidence intervals
post_Fe <- posterior_summary(Fe_m_logn, pars = "^b_", probs = c(0.05, 0.95))

effects_df_Fe <- data.frame(
  term = gsub("^b_", "", rownames(post_Fe)),
  estimate = post_Fe[, "Estimate"],
  l90 = post_Fe[, "Q5"],
  u90 = post_Fe[, "Q95"]
) %>%
  mutate(
    estimate_exp = exp(estimate),
    l90_exp = exp(l90),
    u90_exp = exp(u90),
    analyte = "Fe",
    bayes_R2 = mean(bayes_R2(Fe_m_logn)[, "Estimate"])
  )
```

```{r Fe_effects_table,  echo=FALSE}
# Display effects table
kable(effects_df_Fe %>% select(-analyte), 
      caption = "Fe Model Effects (Log and Exponentiated Scale)",
      digits = 2)
```

```{r Fe_effects_plot, include=FALSE, echo=FALSE, fig.width=8, fig.height=4}
# Plot effects
effects_df_Fe %>%
  filter(term != "Intercept") %>%
  ggplot(aes(x = estimate_exp, y = term)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = l90_exp, xmax = u90_exp), width = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Multiplicative effect (exp(β))",
    y = NULL,
    title = "Fe Model: Effect Sizes",
    subtitle = sprintf("Bayesian R² = %.2f", unique(effects_df_Fe$bayes_R2))
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )
```



Look at solute with TSF, PPT, and flow 

```{r Fe_plot, include=T, echo=FALSE, fig.width=10, fig.height=3}
# Plot effects
tsf_plot <- df_model %>%
  ggplot(aes(y = Fe_QC, x = tsf)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "Days since fire",
    y = "Fe") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

PPT_plot <- df_model %>%
  ggplot(aes(y = Fe_QC, x = lag_C_PPT)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "PPT",
    y = "Fe") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

fow_plot <- df_model %>%
  ggplot(aes(y = Fe_QC, x = flow_filled)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "flow",
    y = "Fe") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

covar_grid <- ggarrange( 
  tsf_plot,
  PPT_plot,
  fow_plot,
  common.legend = T,
  ncol=3,
  nrow=1)

covar_grid

```


#### Mn Model

```{r covar_prep_Mn, cache=TRUE, dependson="data_prep", include=FALSE}

vars <- c("Mn_QC", "lag_C_PPT", "tsf", "flow_filled", "temp", "DO", "EC", "pH", "site")

df_model <- df_WQ_plot %>%
  left_join(new_df_hydro, by = c("site", "date")) %>%
  filter(site != "ophir") %>%
  select(all_of(vars)) %>%
  drop_na() %>%
  mutate(
    catchment = case_when(
      site == "winters_usgs" ~ "winters",
      site == "winters_up" ~ "winters",
      site == "browns" ~ "browns",
      site == "browns_sub" ~ "browns"
    )
  )
```


```{r bayes_priors_Mn, cache=TRUE, dependson="covar_prep",  include=FALSE}

mu0_Mn <- round(log(mean(df_model$Mn_QC, na.rm = TRUE)), 2)

priors_logn_Mn <- c(
  set_prior(sprintf("normal(%f, 2)", mu0_Mn), class = "Intercept"),
  set_prior("normal(0, 1)", class = "b"),
  set_prior("exponential(1)", class = "sd"),
  set_prior("exponential(1)", class = "sigma")
)
```


```{r Mn_bayes_fit, cache=TRUE, dependson="bayes_priors_Mn", include=FALSE}
# Fit or load Mn Bayesian model
Mn_m_logn <- fit_brm(
  model_name = "Mn_lognormal",
  formula = Mn_QC ~ scale(lag_C_PPT) + scale(tsf) + scale(flow_filled) +
                  catchment + (1 | catchment:site),
  data = df_model,
  family = lognormal(),
  prior = priors_logn_Mn
)
```

```{r Mn_diagnostics, include=TRUE, echo=FALSE, fig.width=10, fig.height=6}
# Trace plots
plot(Mn_m_logn)
```

```{r Mn_pp_checks,include=TRUE, echo=FALSE, fig.width=10, fig.height=4}
# Posterior predictive checks
pp_check(Mn_m_logn, ndraws = 100)
# pp_check(Mn_m_logn, type = "hist", ndraws = 5)
```

```{r Mn_results,include=TRUE, echo=FALSE}
library(loo)
# Model summary
summary(Mn_m_logn)

# LOO cross-validation
loo_Mn <- brms::loo(Mn_m_logn)
print(loo_Mn)

# Bayesian R²
r2_Mn <- bayes_R2(Mn_m_logn)
#kable(r2_Mn, caption = "Bayesian R² for Mn Model", digits = 3)
```

```{r Mn_effects_extract, cache=TRUE, dependson="Mn_bayes_fit",  include=FALSE}
# Extract effects and confidence intervals
post_Mn <- posterior_summary(Mn_m_logn, pars = "^b_", probs = c(0.05, 0.95))

effects_df_Mn <- data.frame(
  term = gsub("^b_", "", rownames(post_Mn)),
  estimate = post_Mn[, "Estimate"],
  l90 = post_Mn[, "Q5"],
  u90 = post_Mn[, "Q95"]
) %>%
  mutate(
    estimate_exp = exp(estimate),
    l90_exp = exp(l90),
    u90_exp = exp(u90),
    analyte = "Mn",
    bayes_R2 = mean(bayes_R2(Mn_m_logn)[, "Estimate"])
  )
```

```{r Mn_effects_table,  echo=FALSE}
# Display effects table
kable(effects_df_Mn %>% select(-analyte), 
      caption = "Mn Model Effects (Log and Exponentiated Scale)",
      digits = 2)
```

```{r Mn_effects_plot, include=FALSE, echo=FALSE, fig.width=8, fig.height=4}
# Plot effects
effects_df_Mn %>%
  filter(term != "Intercept") %>%
  ggplot(aes(x = estimate_exp, y = term)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = l90_exp, xmax = u90_exp), width = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Multiplicative effect (exp(β))",
    y = NULL,
    title = "Mn Model: Effect Sizes",
    subtitle = sprintf("Bayesian R² = %.2f", unique(effects_df_Mn$bayes_R2))
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )
```



Look at solute with TSF, PPT, and flow 

```{r Mn_plot, include=T, echo=FALSE, fig.width=10, fig.height=3}
# Plot effects
tsf_plot <- df_model %>%
  ggplot(aes(y = Mn_QC, x = tsf)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "Days since fire",
    y = "Mn") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

PPT_plot <- df_model %>%
  ggplot(aes(y = Mn_QC, x = lag_C_PPT)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "PPT",
    y = "Mn") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

fow_plot <- df_model %>%
  ggplot(aes(y = Mn_QC, x = flow_filled)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "flow",
    y = "Mn") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

covar_grid <- ggarrange( 
  tsf_plot,
  PPT_plot,
  fow_plot,
  common.legend = T,
  ncol=3,
  nrow=1)

covar_grid

```


#### Ba Model

```{r covar_prep_Ba, cache=TRUE, dependson="data_prep", include=FALSE}

vars <- c("Ba_QC", "lag_C_PPT", "tsf", "flow_filled", "temp", "DO", "EC", "pH", "site")

df_model <- df_WQ_plot %>%
  left_join(new_df_hydro, by = c("site", "date")) %>%
  filter(site != "ophir") %>%
  select(all_of(vars)) %>%
  drop_na() %>%
  mutate(
    catchment = case_when(
      site == "winters_usgs" ~ "winters",
      site == "winters_up" ~ "winters",
      site == "browns" ~ "browns",
      site == "browns_sub" ~ "browns"
    )
  )
```


```{r bayes_priors_Ba, cache=TRUE, dependson="covar_prep",  include=FALSE}

mu0_Ba <- round(log(mean(df_model$Ba_QC, na.rm = TRUE)), 2)

priors_logn_Ba <- c(
  set_prior(sprintf("normal(%f, 2)", mu0_Ba), class = "Intercept"),
  set_prior("normal(0, 1)", class = "b"),
  set_prior("exponential(1)", class = "sd"),
  set_prior("exponential(1)", class = "sigma")
)
```


```{r Ba_bayes_fit, cache=TRUE, dependson="bayes_priors_Ba", include=FALSE}
# Fit or load Ba Bayesian model
Ba_m_logn <- fit_brm(
  model_name = "Ba_lognormal",
  formula = Ba_QC ~ scale(lag_C_PPT) + scale(tsf) + scale(flow_filled) +
                  catchment + (1 | catchment:site),
  data = df_model,
  family = lognormal(),
  prior = priors_logn_Ba
)
```

```{r Ba_diagnostics, include=TRUE, echo=FALSE, fig.width=10, fig.height=6}
# Trace plots
plot(Ba_m_logn)
```

```{r Ba_pp_checks,include=TRUE, echo=FALSE, fig.width=10, fig.height=4}
# Posterior predictive checks
pp_check(Ba_m_logn, ndraws = 100)
# pp_check(Ba_m_logn, type = "hist", ndraws = 5)
```

```{r Ba_results,include=TRUE, echo=FALSE}
library(loo)
# Model summary
summary(Ba_m_logn)

# LOO cross-validation
loo_Ba <- brms::loo(Ba_m_logn)
print(loo_Ba)

# Bayesian R²
r2_Ba <- bayes_R2(Ba_m_logn)
r2_Ba
#kable(r2_Ba, caption = "Bayesian R² for Ba Model", digits = 3)
```

```{r Ba_effects_extract, cache=TRUE, dependson="Ba_bayes_fit",  include=FALSE}
# Extract effects and confidence intervals
post_Ba <- posterior_summary(Ba_m_logn, pars = "^b_", probs = c(0.05, 0.95))

effects_df_Ba <- data.frame(
  term = gsub("^b_", "", rownames(post_Ba)),
  estimate = post_Ba[, "Estimate"],
  l90 = post_Ba[, "Q5"],
  u90 = post_Ba[, "Q95"]
) %>%
  mutate(
    estimate_exp = exp(estimate),
    l90_exp = exp(l90),
    u90_exp = exp(u90),
    analyte = "Ba",
    bayes_R2 = mean(bayes_R2(Ba_m_logn)[, "Estimate"])
  )
```

```{r Ba_effects_table,  echo=FALSE}
# Display effects table
kable(effects_df_Ba %>% select(-analyte), 
      caption = "Ba Model Effects (Log and Exponentiated Scale)",
      digits = 2)
```

```{r Ba_effects_plot, include=FALSE, echo=FALSE, fig.width=8, fig.height=4}
# Plot effects
effects_df_Ba %>%
  filter(term != "Intercept") %>%
  ggplot(aes(x = estimate_exp, y = term)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = l90_exp, xmax = u90_exp), width = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Multiplicative effect (exp(β))",
    y = NULL,
    title = "Ba Model: Effect Sizes",
    subtitle = sprintf("Bayesian R² = %.2f", unique(effects_df_Ba$bayes_R2))
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )
```



Look at solute with TSF, PPT, and flow 

```{r Ba_plot, include=T, echo=FALSE, fig.width=10, fig.height=3}
# Plot effects
tsf_plot <- df_model %>%
  ggplot(aes(y = Ba_QC, x = tsf)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "Days since fire",
    y = "Ba") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

PPT_plot <- df_model %>%
  ggplot(aes(y = Ba_QC, x = lag_C_PPT)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "PPT",
    y = "Ba") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

fow_plot <- df_model %>%
  ggplot(aes(y = Ba_QC, x = flow_filled)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "flow",
    y = "Ba") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

covar_grid <- ggarrange( 
  tsf_plot,
  PPT_plot,
  fow_plot,
  common.legend = T,
  ncol=3,
  nrow=1)

covar_grid

```


#### Ca Model

```{r covar_prep_Ca, cache=TRUE, dependson="data_prep", include=FALSE}

vars <- c("Ca_QC", "lag_C_PPT", "tsf", "flow_filled", "temp", "DO", "EC", "pH", "site")

df_model <- df_WQ_plot %>%
  left_join(new_df_hydro, by = c("site", "date")) %>%
  filter(site != "ophir") %>%
  select(all_of(vars)) %>%
  drop_na() %>%
  mutate(
    catchment = case_when(
      site == "winters_usgs" ~ "winters",
      site == "winters_up" ~ "winters",
      site == "browns" ~ "browns",
      site == "browns_sub" ~ "browns"
    )
  )
```


```{r bayes_priors_Ca, cache=TRUE, dependson="covar_prep",  include=FALSE}

mu0_Ca <- round(log(mean(df_model$Ca_QC, na.rm = TRUE)), 2)

priors_logn_Ca <- c(
  set_prior(sprintf("normal(%f, 2)", mu0_Ca), class = "Intercept"),
  set_prior("normal(0, 1)", class = "b"),
  set_prior("exponential(1)", class = "sd"),
  set_prior("exponential(1)", class = "sigma")
)
```


```{r Ca_bayes_fit, cache=TRUE, dependson="bayes_priors_Ca", include=FALSE}
# Fit or load Ca Bayesian model
Ca_m_logn <- fit_brm(
  model_name = "Ca_lognormal",
  formula = Ca_QC ~ scale(lag_C_PPT) + scale(tsf) + scale(flow_filled) +
                  catchment + (1 | catchment:site),
  data = df_model,
  family = lognormal(),
  prior = priors_logn_Ca)
```

```{r Ca_diagnostics, include=TRUE, echo=FALSE, fig.width=10, fig.height=6}
# Trace plots
plot(Ca_m_logn)
```

```{r Ca_pp_checks,include=TRUE, echo=FALSE, fig.width=10, fig.height=4}
# Posterior predictive checks
pp_check(Ca_m_logn, ndraws = 100)
# pp_check(Ca_m_logn, type = "hist", ndraws = 5)
```

```{r Ca_results,include=TRUE, echo=FALSE}
library(loo)
# Model summary
summary(Ca_m_logn)

# LOO cross-validation
loo_Ca <- brms::loo(Ca_m_logn)
print(loo_Ca)

# Bayesian R²
r2_Ca <- bayes_R2(Ca_m_logn)
#kable(r2_Ca, caption = "Bayesian R² for Ca Model", digits = 3)
```

```{r Ca_effects_extract, cache=TRUE, dependson="Ca_bayes_fit",  include=FALSE}
# Extract effects and confidence intervals
post_Ca <- posterior_summary(Ca_m_logn, pars = "^b_", probs = c(0.05, 0.95))

effects_df_Ca <- data.frame(
  term = gsub("^b_", "", rownames(post_Ca)),
  estimate = post_Ca[, "Estimate"],
  l90 = post_Ca[, "Q5"],
  u90 = post_Ca[, "Q95"]
) %>%
  mutate(
    estimate_exp = exp(estimate),
    l90_exp = exp(l90),
    u90_exp = exp(u90),
    analyte = "Ca",
    bayes_R2 = mean(bayes_R2(Ca_m_logn)[, "Estimate"])
  )
```

```{r Ca_effects_table,  echo=FALSE}
# Display effects table
kable(effects_df_Ca %>% select(-analyte), 
      caption = "Ca Model Effects (Log and Exponentiated Scale)",
      digits = 2)
```

```{r Ca_effects_plot, include=FALSE, echo=FALSE, fig.width=8, fig.height=4}
# Plot effects
effects_df_Ca %>%
  filter(term != "Intercept") %>%
  ggplot(aes(x = estimate_exp, y = term)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = l90_exp, xmax = u90_exp), width = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Multiplicative effect (exp(β))",
    y = NULL,
    title = "Ca Model: Effect Sizes",
    subtitle = sprintf("Bayesian R² = %.2f", unique(effects_df_Ca$bayes_R2))
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )
```




Look at solute with TSF, PPT, and flow 

```{r Ca_plot, include=T, echo=FALSE, fig.width=10, fig.height=3}
# Plot effects
tsf_plot <- df_model %>%
  ggplot(aes(y = Ca_QC, x = tsf)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "Days since fire",
    y = "Ca") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

PPT_plot <- df_model %>%
  ggplot(aes(y = Ca_QC, x = lag_C_PPT)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "PPT",
    y = "Ca") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

fow_plot <- df_model %>%
  ggplot(aes(y = Ca_QC, x = flow_filled)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "flow",
    y = "Ca") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

covar_grid <- ggarrange( 
  tsf_plot,
  PPT_plot,
  fow_plot,
  common.legend = T,
  ncol=3,
  nrow=1)

covar_grid

```



#### Al Model

```{r covar_prep_Al, cache=TRUE, dependson="data_prep", include=FALSE}

vars <- c("Al_QC", "lag_C_PPT", "tsf", "flow_filled", "temp", "DO", "EC", "pH", "site")

df_model <- df_WQ_plot %>%
  left_join(new_df_hydro, by = c("site", "date")) %>%
  filter(site != "ophir") %>%
  select(all_of(vars)) %>%
  drop_na() %>%
  mutate(
    catchment = case_when(
      site == "winters_usgs" ~ "winters",
      site == "winters_up" ~ "winters",
      site == "browns" ~ "browns",
      site == "browns_sub" ~ "browns"
    )
  )
```


```{r bayes_priors_Al, cache=TRUE, dependson="covar_prep",  include=FALSE}

mu0_Al <- round(log(mean(df_model$Al_QC, na.rm = TRUE)), 2)

priors_logn_Al <- c(
  set_prior(sprintf("normal(%f, 2)", mu0_Al), class = "Intercept"),
  set_prior("normal(0, 1)", class = "b"),
  set_prior("exponential(1)", class = "sd"),
  set_prior("exponential(1)", class = "sigma")
)
```


```{r Al_bayes_fit, cache=TRUE, dependson="bayes_priors_Al", include=FALSE}
# Fit or load Al Bayesian model
Al_m_logn <- fit_brm(
  model_name = "Al_lognormal",
  formula = Al_QC ~ scale(lag_C_PPT) + scale(tsf) + scale(flow_filled) +
                  catchment + (1 | catchment:site),
  data = df_model,
  family = lognormal(),
  prior = priors_logn_Al
)
```

```{r Al_diagnostics, include=TRUE, echo=FALSE, fig.width=10, fig.height=6}
# Trace plots
plot(Al_m_logn)
```

```{r Al_pp_checks,include=TRUE, echo=FALSE, fig.width=10, fig.height=4}
# Posterior predictive checks
pp_check(Al_m_logn, ndraws = 100)
# pp_check(Al_m_logn, type = "hist", ndraws = 5)
```

```{r Al_results,include=TRUE, echo=FALSE}
library(loo)
# Model summary
summary(Al_m_logn)

# LOO cross-validation
loo_Al <- brms::loo(Al_m_logn)
print(loo_Al)

# Bayesian R²
r2_Al <- bayes_R2(Al_m_logn)
#kable(r2_Al, caption = "Bayesian R² for Al Model", digits = 3)
```

```{r Al_effects_extract, cache=TRUE, dependson="Al_bayes_fit",  include=FALSE}
# Extract effects and confidence intervals
post_Al <- posterior_summary(Al_m_logn, pars = "^b_", probs = c(0.05, 0.95))

effects_df_Al <- data.frame(
  term = gsub("^b_", "", rownames(post_Al)),
  estimate = post_Al[, "Estimate"],
  l90 = post_Al[, "Q5"],
  u90 = post_Al[, "Q95"]
) %>%
  mutate(
    estimate_exp = exp(estimate),
    l90_exp = exp(l90),
    u90_exp = exp(u90),
    analyte = "Al",
    bayes_R2 = mean(bayes_R2(Al_m_logn)[, "Estimate"])
  )
```


```{r Al_effects_table,  echo=FALSE}
# Display effects table
kable(effects_df_Al %>% select(-analyte), 
      caption = "Al Model Effects (Log and Exponentiated Scale)",
      digits = 2)
```

```{r Al_effects_plot, include=FALSE, echo=FALSE, fig.width=8, fig.height=4}
# Plot effects
effects_df_Al %>%
  filter(term != "Intercept") %>%
  ggplot(aes(x = estimate_exp, y = term)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = l90_exp, xmax = u90_exp), width = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Multiplicative effect (exp(β))",
    y = NULL,
    title = "Al Model: Effect Sizes",
    subtitle = sprintf("Bayesian R² = %.2f", unique(effects_df_Al$bayes_R2))
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

```



Look at solute with TSF, PPT, and flow 

```{r Al_plot, include=T, echo=FALSE, fig.width=10, fig.height=3}
# Plot effects
tsf_plot <- df_model %>%
  ggplot(aes(y = Al_QC, x = tsf)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "Days since fire",
    y = "Al") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

PPT_plot <- df_model %>%
  ggplot(aes(y = Al_QC, x = lag_C_PPT)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "PPT",
    y = "Al") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

fow_plot <- df_model %>%
  ggplot(aes(y = Al_QC, x = flow_filled)) +
  geom_point(aes(color=tsf)) +
  labs(
    x = "flow",
    y = "Al") +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

covar_grid <- ggarrange( 
  tsf_plot,
  PPT_plot,
  fow_plot,
  common.legend = T,
  ncol=3,
  nrow=1)

covar_grid

```



#### As Model

```{r covar_prep_As, cache=TRUE, dependson="data_prep", include=FALSE}

vars <- c("As_QC", "lag_C_PPT", "tsf", "flow_filled", "temp", "DO", "EC", "pH", "site")

df_model <- df_WQ_plot %>%
  left_join(new_df_hydro, by = c("site", "date")) %>%
  filter(site != "ophir") %>%
  select(all_of(vars)) %>%
  drop_na() %>%
  mutate(
    catchment = case_when(
      site == "winters_usgs" ~ "winters",
      site == "winters_up" ~ "winters",
      site == "browns" ~ "browns",
      site == "browns_sub" ~ "browns"
    )
  )
```


```{r bayes_priors_As, cache=TRUE, dependson="covar_prep",  include=FALSE}

mu0_As <- round(log(mean(df_model$As_QC, na.rm = TRUE)), 2)

priors_logn_As <- c(
  set_prior(sprintf("normal(%f, 2)", mu0_As), class = "Intercept"),
  set_prior("normal(0, 1)", class = "b"),
  set_prior("exponential(1)", class = "sd"),
  set_prior("exponential(1)", class = "sigma")
)
```


```{r As_bayes_fit, cache=TRUE, dependson="bayes_priors_As", include=FALSE}
# Fit or load Al Bayesian model
As_m_logn <- fit_brm(
  model_name = "As_lognormal",
  formula = As_QC ~ scale(lag_C_PPT) + scale(tsf) + scale(flow_filled) +
                  catchment + (1 | catchment:site),
  data = df_model,
  family = lognormal(),
  prior = priors_logn_As
)
```

```{r As_diagnostics, include=TRUE, echo=FALSE, fig.width=10, fig.height=6}
# Trace plots
plot(As_m_logn)
```

```{r As_pp_checks,include=TRUE, echo=FALSE, fig.width=10, fig.height=4}
# Posterior predictive checks
pp_check(As_m_logn, ndraws = 100)
# pp_check(As_m_logn, type = "hist", ndraws = 5)
```

```{r As_results,include=TRUE, echo=FALSE}
library(loo)
# Model summary
summary(As_m_logn)

# LOO cross-validation
loo_As <- brms::loo(As_m_logn)
print(loo_As)

# Bayesian R²
r2_As <- bayes_R2(As_m_logn)
#kable(r2_As, caption = "Bayesian R² for Al Model", digits = 3)
```

```{r As_effects_extract, cache=TRUE, dependson="As_bayes_fit",  include=FALSE}
# Extract effects and confidence intervals
post_As <- posterior_summary(As_m_logn, pars = "^b_", probs = c(0.05, 0.95))

effects_df_As <- data.frame(
  term = gsub("^b_", "", rownames(post_As)),
  estimate = post_As[, "Estimate"],
  l90 = post_As[, "Q5"],
  u90 = post_As[, "Q95"]
) %>%
  mutate(
    estimate_exp = exp(estimate),
    l90_exp = exp(l90),
    u90_exp = exp(u90),
    analyte = "Al",
    bayes_R2 = mean(bayes_R2(As_m_logn)[, "Estimate"])
  )
```


```{r As_effects_table,  echo=FALSE}
# Display effects table
kable(effects_df_As %>% select(-analyte), 
      caption = "Al Model Effects (Log and Exponentiated Scale)",
      digits = 2)
```

```{r As_effects_plot, include=FALSE, echo=FALSE, fig.width=8, fig.height=4}
# Plot effects
effects_df_As %>%
  filter(term != "Intercept") %>%
  ggplot(aes(x = estimate_exp, y = term)) +
  geom_point(size = 3) +
  geom_errorbar(aes(xmin = l90_exp, xmax = u90_exp), width = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Multiplicative effect (exp(β))",
    y = NULL,
    title = "Al Model: Effect Sizes",
    subtitle = sprintf("Bayesian R² = %.2f", unique(effects_df_As$bayes_R2))
  ) +
  theme_classic() +
  theme(
    axis.text = element_text(size = 11),
    plot.title = element_text(face = "bold")
  )

```

---


---

## Combined Results

```{r combine_effects,  cache=TRUE, include=FALSE}
# Combine all analyte effects (assuming all models have been fit)
coeff_plt_df <- rbind(
  effects_df_TSS,
  effects_df_DOC,
  effects_df_TDN,
  effects_df_PO4.P,
  effects_df_Sr,
  effects_df_Fe,
  effects_df_Mn,
  effects_df_Ba,
  effects_df_Ca,
  effects_df_Al)
# 
# # Save combined results
# write_csv(coeff_plt_df, file.path(proc_data_dir, "coeff_plt_df.csv"))

```

```{r final_coefficient_plot,  include=TRUE, echo=FALSE, fig.width=9, fig.height=9}
# Create publication-quality coefficient plot
# (This code assumes coeff_plt_df exists from all fitted models)

analyte_order <- coeff_plt_df %>%
 # filter(analyte %in% c("PO4.P", "TDN", "DOC", "TSS")) %>%
  group_by(analyte) %>%
  summarise(bayes_R2_analyte = mean(bayes_R2, na.rm = TRUE), .groups = "drop") %>%
  arrange(desc(bayes_R2_analyte)) %>%
  pull(analyte)

model_plt <- coeff_plt_df %>%
 # filter(analyte %in% c("PO4.P", "TDN", "DOC", "TSS")) %>%
  filter(term != "Intercept", term != "catchmentwinters") %>%
  mutate(analyte = factor(analyte, levels = analyte_order)) %>%
  ggplot(aes(x = estimate_exp, y = term, color = bayes_R2, 
             shape = term)) +
  geom_vline(xintercept = 1, linetype = 2) +
  geom_errorbarh(aes(xmin = l90_exp, xmax = u90_exp), height = 0) +
  geom_point(size = 3) +
  facet_grid(analyte ~ .) +
  scale_x_log10() +
  labs(
    x = "Scaled effect on solute concentration",
    y = NULL
  ) +
  scale_y_discrete(labels = c(
    scalelag_C_PPT = expression(beta["Precipitation"]),
    scaletsf = expression(beta["Days since fire"]),
    scaleflow_filled = expression(beta["Flow"])
  )) +
  scale_color_viridis_c(option = "viridis", 
                              direction = -1,
                        name = "Bayes R²") +
  scale_shape_discrete(
    name = "Predictor",
    labels = c(
      scalelag_C_PPT = "Precipitation",
      scaletsf = "Days since fire",
      scaleflow_filled = "Flow"
    )
  ) +
  theme_classic() +
  theme(
    axis.text.y = element_text(size = 14),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  )

print(model_plt)

# #Save figure
# ggsave(
#   filename = file.path(fig_dir, "ERDC_coeff_plts_GPHS.png"),
#   plot = model_plt,
#   width = 5.25,
#   height = 7.5,
#   dpi = 300
# )

```

```{r, echo=FALSE, include =F}
# ggsave(plot = DMCres_grid_metals, filename = paste("./Users/kellyloria/Documents/DRI/ERDC_Davis_Fire/Figures/DMLC_res_metals_grid_plot_SI.png",sep=""),width=6,height=20,dpi=300)

```


## Session Info

```{r session_info, echo=FALSE}
sessionInfo()
```

End of script. 
